mode speeds used in the ithim-global model

### 2020-11-21 code/trips_analysis/mode_speed_summary.Rmd
change default speeds to mean of median speeds for cities

## 3. Conclusions on default speeds
- Walking: use median speeds for all cities split by sex 
- Cycling: Use median speeds split by sex
- Cycled Rickshaw should be 2/3 the speed of bicycle
- Motorcycle Rickshaw should be 2/3 the speed of motorcycle
- Van should be the same as bus
- Others:  use same median speeds for both sex and age

@@

default_speeds <- list(
    bus=10.8,
    bus_driver=10.8,
    minibus=10.8,
    minibus_driver=10.8,
    car=11.3,
    taxi=11.3,
    pedestrian_male=4,
    pedestrian_female=3,
    walk_to_pt=10,
    cycle_male=8,
    cycle_female=6,
    motorcycle=12,
    truck=10.8,
    van=10.8,
    subway=12.9,
    rail=13.5,
    auto_rickshaw=8,
    shared_auto=11.3,
    shared_taxi=11.3,
    cycle_rickshaw=5.3
  )

>>>>

## 3. Conclusions on default speeds
- Walking: use median speeds for all cities split by sex 
- Cycling: Use median speeds split by sex
- Cycled Rickshaw should be 2/3 the speed of bicycle
- Motorcycle Rickshaw should be 2/3 the speed of motorcycle
- Van should be the same as car
- Others:  use same median speeds for both sex and age

@@

default_speeds <- list(
    bus=10.8,
    bus_driver=10.8,
    minibus=10.8,
    minibus_driver=10.8,
    car=11.3,
    taxi=11.3,
    pedestrian_male=4,
    pedestrian_female=3,
    walk_to_pt=10,
    cycle_male=8,
    cycle_female=6,
    motorcycle=12,
    truck=10.8,
    van=11.3,
    subway=12.9,
    rail=13.5,
    auto_rickshaw=8,
    shared_auto=11.3,
    shared_taxi=11.3,
    cycle_rickshaw=5.3
  )
